\section{Conclusion}

In this project it has been shown that in general, proper orthochronous Lorentz transformations (POLTs) have two invariant null directions in Minkowskian space-time. The special case where both of these coincide, known as the singular case, has been investigated. Starting from the Schwarzschild solution of the vacuum field equations a strange line element was derived and shown to be the Minkowskian line element with $m = 0$, as in Eqn.(\ref{Kasner_after_limit_no_k}). A Lorentz quadratic form preserving transformation on this line element was found to have two parameters and to be a singular Lorentz transformation. Thus it was shown that all singular Lorentz transformations are two parameter abelian subgroups of the Lorentz group. A connection between $2 \times 2$ Hermitian matrices and points in Minkowskian space-time was then established, from which it was shown that there is a two to one correspondence between $SL(2,\mathbb{C})$ matrices and POLTs. Then a coordinate transformation between the sphere $\mathbb{S}^2$ and the extended complex plane $\hat{\mathbb{C}}$ was used to relate Minkowskian space time to $\hat{\mathbb{C}}$. A POLT in these coordinates was then shown to derive the fractional linear transformation, or Mobius transformation of Eqn.(\ref{Extended_Complex_Fractional_Linear_Transformation}), thus there is a one to one correspondence between POLTs and fractional linear transformations. Also this can be understood as an isomorphism between the proper orthochronous Lorentz group and the Mobius group. It was then shown that the fractional linear form of the infinitesimal Lorentz transformations is equivalent to the Lorentz force and thus a connection was made between $L_{ij}$ and the electromagnetic tensor, usually denoted by $F_{ij}$. When the fractional linear form of the infinitesimal Lorentz transformations was constructed it was clear that there were a number of cases, each with either one or two fixed null directions. Of interest to this project was the singular case, thus the condition $a^2 + bc = 0$ was established. By writing this condition in terms of the electric and magnetic fields in the electromagnetic tensor the conditions for a pure radiation field, Eqn(\ref{Infinitesimal_Pure_Rad_Cond_1}) and (\ref{Infinitesimal_Pure_Rad_Cond_2}) emerged. By then writing the condition for a singular Lorentz transformation in the coordinates of Minkowskian space-time it was shown that the singular null direction, $k^i$ was in fact the direction of propagation of the pure radiation field. Finally, it was proven that the electric and magnetic fields and the singular null direction form an orthonormal triad.     
